\plaintitle

### 2016-09-21 drafts/labor/discussion.tex

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Discussion}
\topic{Having taken a comprehensive look toward crowd work through the piecework lens,
we can't help but take a step back to consider a number of meta--issues that arose in our analysis.}
Stated briefly, these issues are 
\begin{inlinelist}
  \item \namerefl{sec:perilousProblemsPredicting},
  \item \namerefl{sec:polarizationOfCrowdWork}, and
  \item \namerefl{sec:whatShouldBeTheFuture}.
\end{inlinelist}
We will attempt to grapple with these questions here based on
what we brought up in the earlier case studies.

@@

\topic{Perhaps the most pressing question is this:
is the future of crowd work going to look more \textit{Dystopian} or \textit{Utopian}?}
% The unsatisfying answer is that
If we have learn nothing, crowd work will probably end up somewhere in the middle.
% It's possible that the difficulties of enforcing laws on multinational corporations is
% tipping the balance of power in the direction of corporations, in which case
% things will get worse;
% but arguably we can affect change on the trajectory of crowd work,
% benefiting from everything piecework scholars have learned about
% collective action and governance
% among workers, while also avoiding some of the perils they faced.

\subsection{Deciding our Research Agenda}\label{sec:whatShouldBeTheFuture}
\begin{enumerate}
  \item We need to take a step back from the work that's been done so far and
        think about where we are going with the crowd work research agenda.
  \item Piecework researchers pointed out long ago that piecework is problematized by the fact that
        ``piecework does not compensate workers for time spent switching tasks''
        \cite{bewley1999wages} --- we've studied this phenomenon in crowd work
        \cite{delayAndOrderLasecki,taskSearch}
        and we should consider whether this remains a worthwhile area to explore unless
        we're actually finding ways to minimize the many forms of costs of switching tasks.
  \item What questions are we trying to answer?
        If, as we assumed in
        the previous section on \namerefl{sec:polarizationOfCrowdWork},
        our driving motivation is to empower workers, we

\end{enumerate}

>>>>

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\onlyinsubfile{
\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument{complexity}
\externaldocument{relationships}
\externaldocument{decomposition}
}

\begin{document}
\section{Discussion}
\topic{Having taken a comprehensive look toward crowd work through the piecework lens,
we can't help but take a step back to consider a number of meta--issues that arose in our analysis.}
Stated briefly, these issues are 
\begin{inlinelist}
  \item \namerefl{sec:perilousProblemsPredicting},
  \item \namerefl{sec:polarizationOfCrowdWork}, and
  \item \namerefl{sec:whatShouldBeTheFuture}.
\end{inlinelist}
We will attempt to grapple with these questions here based on
what we brought up in the earlier case studies.

@@

\topic{Perhaps the most pressing question is this:
is the future of crowd work going to look more \textit{Dystopian} or \textit{Utopian}?}
If we have learn nothing, crowd work will probably end up somewhere in the middle.
It's possible that the difficulties of enforcing laws on multinational corporations is
tipping the balance of power in the direction of corporations, in which case
things will get worse;
but arguably we can affect change on the trajectory of crowd work,
benefiting from everything piecework scholars have learned about
collective action and governance
among workers, while also avoiding some of the perils they faced.
\ali{I really don't like this paragraph, but I felt like we needed to plant a flag on the question in the topic sentence}

\subsection{Determining our Research Agenda}\label{sec:whatShouldBeTheFuture}
Taking a step back from the work that's been done so far and
thinking about where the body of crowd work research is attempting to go may help us identify
areas of research on which we should be pushing forward on.
We return to the three questions that motivated this paper:
\begin{inlinelist}
  \item ``\namerefl{sec:complexity}?''
  \item ``\namerefl{sec:decomposition}?''
        and
  \item ``\namerefl{sec:relationships}?''
\end{inlinelist}.

While we have arguably outpaced piecework with regard to the limits on the complexity of work,
we have yet to find insurmountable limits to crowdsourcing.
Still, we can learn from the piecework literature as it relates to
the stymieing effect that mismanagement has on workers;
research into the complexity limits should emphasize on finding new ways to manage workers,
in particular using humans --- perhaps other crowd workers ---
to act as modern foremen.

Piecework researchers looking into decomposition pointed out long ago that
piecework is saddled by a lower limit on decomposition:
``piecework does not compensate workers for time spent switching tasks''
\cite{bewley1999wages}.
We've since studied this phenomenon in crowd work to great length both
observationally \cite{taskSearch} and
experimentally \cite{delayAndOrderLasecki}.
We should consider whether this remains a worthwhile area to explore; %  unless
% we're actually finding ways to minimize the many forms of costs of switching tasks.
unless the work we put forth directly affects the costs of task--switching
--- for instance, the cost of suboptimal task search, or the cognitive burden of changing tasks ---
we may only make incremental advances in micro--task decomposition.

Finally, we turn to the relationships of crowd workers.
The crowd work literature here can convincingly speak back to
the piecework scholarship perhaps more than in the other sections.
The tools that are available to us today
--- not just technical, but \textit{methodological} ---
make it possible to
discover,
study, and
empower \ali{I feel like Lily would take some umbrage at this because she seemed to not like the narrative of us researchers just unilaterally bequeathing power upon Turkers (well, Turkers certainly disliked it). Thoughts on refactoring?}
crowd workers in ways that were unimaginable to piecework researchers.
A professor engages in crowd work \cite{bighamHalfWorkday}
not just because it's possible, but because our community
(of mostly computer scientists)
appreciates the importance of approaches such as participant--observation and ethnography as a whole
\cite{olson2014ways}.
% Whereas piecework didn't have the benefit of Anthropology as we know it or the myriad ways of discovering, learning about, and empowering workers
% What questions are we trying to answer?
% If, as we assumed in
% the previous section on \namerefl{sec:polarizationOfCrowdWork},
% our driving motivation is to empower workers, we

% \end{enumerate}
